Meta RL analyses

### 2019-02-12 meta_RL_analyses.Rmd
Better naming of run types for plots

```{r}
num_runs = 5
results_dir = "results/paper_results/"

@@

@@

```{r}
summary_plot(reward_d %>%
               filter(epoch == 0,
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ run_type)
ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3)
```

>>>>

```{r}
num_runs = 10
results_dir = "results/paper_results/"

@@

name_run_type = function(run_type) { # names for plotting
  case_when(run_type == "basic" ~ "Targeted 10% holdout",
            run_type == "basic_random_holdout_longer" ~ "Random 50% holdout",
            T ~ run_type)
}

@@

```{r}
summary_plot(reward_d %>%
               filter(epoch == 0,
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ named_run_type)
ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3)
```
